---
title: "HOMER_ANALYSIS"
author: "Amarise Silié"
date: "2024-03-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries

Install as needed with `install.packages("namelib")`, where `namelib` is the name of the library, or `BiocManager::install("NAME")`. Optionally try: `BiocManager::install("NAME", force=TRUE, lib = "/home/USER/R/x86_64-pc-linux-gnu-library/X.X")` if you encounter errors.

```{r include=FALSE}
# developed in R 4.3.2

library(biomaRt) # v2.58.2, to generate gene lengths
library(data.table) # v1.15.2, data storage
library(stringi) # v1.8.3, for data manipulation
library(ggplot2) # v3.5.0, for making figures
library(tidyverse) # v2.0.0, data storage and manipulation, making figures
library(scales) # v1.3.0, for making figures
library(ggrepel) # v0.9.5 for making figures
library(randomcoloR) # v1.1.0.1, for generation of palettes
```

# Load data

Loading the HOMER annotation files. I load each file separately (which is less convenient if you have many files, but in my case is doable). Make sure to set your work directory correctly to save the upcoming figures in the right folders. You can also specify the general path of your annotation data and the folder where you want to save your graphs below:

```{r}
# path to data
general_path <- '/path/to/data/' # <- do not forget the last /
# path to save figures to
save_path <- '/path/to/save/figures/' # <- do not forget the last /

# this is how we will save our plots later:
paste(save_path, 'name', sep='')
```

If a directory does not exist yet, **Rstudio will ask you whether you want to it to create the directory for you *in the console!***

```{r}
macs_gof_3 <- read.delim(paste(general_path, "macs2_gof_3_T1_annotatePeaks.txt", sep=''))
macs_gof_4 <- read.delim(paste(general_path, "macs2_gof_4_T1_annotatePeaks.txt", sep=''))
macs_gof_5 <- read.delim(paste(general_path, "macs2_gof_5_T1_annotatePeaks.txt", sep=''))
macs_wt_3 <- read.delim(paste(general_path, "macs2_wt_3_T1_annotatePeaks.txt", sep=''))
macs_wt_4 <- read.delim(paste(general_path, "macs2_wt_4_T1_annotatePeaks.txt", sep=''))
macs_wt_5 <- read.delim(paste(general_path, "macs2_wt_5_T1_annotatePeaks.txt", sep=''))

pureclip_gof_3 <- read.delim(paste(general_path, "pureclip_gof_3_T1_annotatePeaks.txt", sep=''))
pureclip_gof_4 <- read.delim(paste(general_path, "pureclip_gof_4_T1_annotatePeaks.txt", sep=''))
pureclip_gof_5 <- read.delim(paste(general_path, "pureclip_gof_5_T1_annotatePeaks.txt", sep=''))
pureclip_wt_3 <- read.delim(paste(general_path, "pureclip_wt_3_T1_annotatePeaks.txt", sep=''))
pureclip_wt_4 <- read.delim(paste(general_path, "pureclip_wt_4_T1_annotatePeaks.txt", sep=''))
pureclip_wt_5 <- read.delim(paste(general_path, "pureclip_wt_5_T1_annotatePeaks.txt", sep=''))

# all tables to be combined later
dfs <- list( #macs_gof_3, macs_gof_4, macs_gof_5, macs_wt_3, macs_wt_4, macs_wt_5, 
           pureclip_gof_3, pureclip_gof_4, pureclip_gof_5, pureclip_wt_3, pureclip_wt_4, pureclip_wt_5)
names <- c( # "macs_gof_3", "macs_gof_4", "macs_gof_5", "macs_wt_3", "macs_wt_4", "macs_wt_5",
           "pureclip_gof_3", "pureclip_gof_4", "pureclip_gof_5", "pureclip_wt_3", "pureclip_wt_4", "pureclip_wt_5")
```

# Preparing the dataframe

```{r}
# joining all tables in a single dataframe
count <- 1
df_combined <- data.frame()

for (df in dfs){
  # add sample name
  df <- mutate(df, sample = names[count])
  # change name of the first column (for simplicity)
  names(df)[1] <- "peak_ID"
  count <- count + 1
  # combine all the dataframes
  df_combined <- bind_rows(df_combined, df)
}

df_combined
```

## Adding columns

Adding: simplified annotation, number of peaks per Entrez.ID, gene length of each Entrez.ID, normalized peak count, peak score \* peak count, peak score \* normalized peak count.

```{r include=FALSE}
# simple annotation -> important for basic annotation (piecharts)
df_combined$simple_annotation <- gsub(" .*$", "", df_combined$Annotation)

# peak_count (or crosslink count) per Entrez.ID
df_combined <-
  df_combined |>
  # we do the following per sample:
  group_by(sample, Entrez.ID, .drop = FALSE) |> 
  # count per gene (entrez.id) how many peaks/crosslinks it has 
  add_count(Entrez.ID, name = 'peak_count') |> 
  distinct() # remove duplicate rows

# gene_length (in bp)
gene_list <- unique(df_combined$Entrez.ID) # get genes
human <- useMart("ensembl", dataset="hsapiens_gene_ensembl") # get db
gene_coords=getBM(attributes=c("hgnc_symbol","ensembl_gene_id", "start_position","end_position"),
                  filters="ensembl_gene_id", values=gene_list, mart=human)
# calculate gene_length
gene_coords$gene_length=gene_coords$end_position - gene_coords$start_position

# add gene_length column to df_combined
df_combined <- left_join(df_combined, gene_coords[c("ensembl_gene_id", "gene_length")],
                                 by = c("Entrez.ID" = "ensembl_gene_id"))
```

```{r}
# norm_peakcount_bylength: apply normalization by doing # peaks / length
df_combined$norm_peakcount_bylength <- df_combined$peak_count / df_combined$gene_length

# intensityxcount: peak.score x peak_count
df_combined$intensityxcount <- df_combined$Peak.Score * df_combined$peak_count

# intensityxnormpeak: peak.score x norm_peakcount_bylength
df_combined$intensityxnormpeak <- df_combined$Peak.Score * df_combined$norm_peakcount_bylength
```

## Removing columns/rows

```{r}
df_combined <- df_combined[, !colnames(df_combined) %in% c("Nearest.Refseq", "Nearest.Ensembl", "Nearest.Unigene", "Focus.Ratio.Region.Size", "Gene.Alias", "Gene.Description")]

# empty cells = NA
df_combined[df_combined == ""] <- NA
# rows with empty Entrez.IDs --> removed
df_combined <- df_combined %>%
  filter(!is.na(Entrez.ID))
```

## Saving the table

```{r}
file_path <- paste(save_path, 'df_combined_nocontrol.tsv', sep='')
write.table(df_combined, file=file_path, quote=FALSE, sep='\t')
```

# Basic Annotation (Piecharts)

HOMER assigns annotations to each peak in the following priority order: TSS, TTS, Exon, Intron, Intergenic.

```{r echo=FALSE, fig.align="center", fig.width=10, message=FALSE, warning=FALSE}
# omit rows where simple_annotation = NA
df_combined[!is.na(df_combined$simple_annotation),] %>% 
  group_by(sample) %>% 
  count(simple_annotation, sample) %>% 
  
  # plot
  ggplot(aes(x = "", y = n, fill = simple_annotation)) +
  geom_bar(stat = "identity", width = 1, color = "white", position = position_fill()) +
  geom_text(aes(label = n), position = position_fill(vjust = 0.5)) +
  coord_polar(theta = "y", start = 0) +
  facet_wrap(~ sample) +
  ggtitle('Number of PureCLIP peaks corresponding to types (no control)') +
  # remove background, grid, numeric labels
  theme_void()

  # save figure
ggsave(paste(save_path, "basic_annotation_piechart/pureclip.png", sep=''), bg = 'white')
```

## Filtering out Intergenic hits

Intergenic regions are, to our knowledge, not transcribed (**not true!**). As we are only interested in regions that can encode for RNA, we filter out the intergenic hits. You can comment this code block if you prefer to keep the intergenic hits.

```{r}
# to see how much you're filtering out:
df_combined %>% filter(simple_annotation == 'Intergenic')

# actual filtering:
# df_combined <- df_combined %>% filter(simple_annotation == 'Intergenic')
```

## Color assignment

```{r}
# # To generate a random list of 35 colors:
# myColor <- randomcoloR::distinctColorPalette(k = 35)

myColor <- c("#C2EABD", "#ECD194", "#B5E8E3", "#55E698", "#F24C3D", "#DB6A6B", "#E4AFD0", "#B4BFE5", "#A2AA67", "#8D9498" ,"#63E452","#63CDE1", "#E1478F", "#D034E8", "#DCB945", "#C2F040", "#619872" ,"#7936E7", "#D8A397", "#E5DBE6", "#E641C5", "#E78EDD", "#6D7FDD", "#69E8D1", "#BE6DDD", "#E09454" ,"#E7E248", "#B29CDD", "#C4709B", "#6D57CF", "#6197D5", "#E3DFC6")
types <- unique(df_combined$Gene.Type)
types <- types[order(names(setNames(types, types)))]
names(myColor) <- types
myColor
```

# Peak counts (Boxplots)

```{r fig.height=4, fig.width=8}
# peak counts per sample
peak_counts <- data.frame(table(df_combined$sample))
# condition
peak_counts$condition <- c(rep("gof",3),rep("wt",3))

ggplot(peak_counts, aes(x=as.factor(condition), y=Freq)) + 
    geom_boxplot(fill="slateblue", alpha=0.2) + 
    geom_jitter(color="blue", size=1, alpha=0.9, 
                position = position_jitter(height = .1, width = .1)) +
    # coord_cartesian(ylim = c(0, 3500)) + # define range
    xlab("condition") +
    ylab("peak count")

  # save figure
ggsave(paste(save_path, "boxplots/pureclip_peak_count.png", sep=''))
```

# Gene types of peaks (Barplots)

Note: A gene can contain multiple crosslink sites (in this case 1 peak = 1 crosslink), thus multiple peaks. Therefore, some gene types may be overrepresented in these barplots.

```{r echo=FALSE, fig.align="center", fig.width=15, message=FALSE, warning=FALSE}

# omit rows where Gene.Type = NA
df_combined[!is.na(df_combined$Gene.Type),] %>%
  group_by(sample) %>%
  count(Gene.Type, sample) %>%
  # change order of gene type appearances in barplot
  mutate(Gene.Type = fct_reorder2(Gene.Type, sample, n))  %>%

  # fraction plot
  ggplot(aes(x = sample, y = n)) +
    geom_bar(aes(fill = Gene.Type), width = 0.7,
             position="fill", stat="identity",
             colour="black") +
    theme(text = element_text(size=12)) + # change font size
    scale_fill_manual(values = myColor) + # change colors
    coord_flip() + # horizontal graph
    scale_y_continuous(labels = percent_format(accuracy = 1),
                       breaks = breaks_pretty(10)) + # percentages
    ggtitle("Gene types of peaks in fractions") +
    ylab("Fraction")

  # save figure
ggsave(paste(save_path, "gene_types_barplots/pureclip_peaks_fraction.png", sep=''))

# omit rows where Gene.Type = NA
df_combined[!is.na(df_combined$Gene.Type),] %>%
  group_by(sample) %>%
  count(Gene.Type, sample) %>%
  # change order of gene type appearances in barplot
  mutate(Gene.Type = fct_reorder2(Gene.Type, sample, n))  %>%

  # absolute plot
  ggplot(aes(x = sample, y = n )) +
    geom_col(aes(fill = Gene.Type), width = 0.7, colour="black") +
    geom_bar(position="fill", stat="identity") +
    theme(text = element_text(size=12)) +
    scale_fill_manual(values = myColor) +
    coord_flip() +
    scale_y_continuous(breaks = breaks_pretty(10)) +
    ggtitle("Gene types of peaks in counts")

  # save figure
ggsave(paste(save_path, "gene_types_barplots/pureclip_peaks_absolute.png", sep=''))

```

# Gene lists

If you want to do some GO pathway analysis, e.g. using ggprofiler, you can generate gene lists. If you have two different conditions, e.g. wild type vs. gain-of-function (as in my case), you can take the differences between these lists.

If `write.table` throws an error, create the `genes` folder in the desired directory and run again.

```{r message=FALSE, warning=FALSE, include=FALSE}
# creating a genes folder so write.table() does not throw an error
dir.create(paste(save_path, 'genes', sep=''), showWarnings = FALSE)

# gof genes
gof_genes <- df_combined %>%
  subset(grepl("pureclip_gof_*",sample)) %>%
  {unique(.$Entrez.ID)}
  
# wt_genes
wt_genes <- df_combined %>%
  subset(grepl("pureclip_wt_*",sample)) %>%
  {unique(.$Entrez.ID)}

# collect genes unique to either gof or wt
gof_only <- gof_genes[!(gof_genes %in% wt_genes)]
wt_only <- wt_genes[!wt_genes %in% gof_genes]

# save to .txt
# if this fails, make the genes folder first
write.table(gof_genes, file=paste(save_path, "genes/gof_gene_list.txt", sep=''), 
            sep=",", row.names = FALSE, quote=FALSE)
write.table(gof_only, file=paste(save_path, "genes/gof_only_gene_list.txt", sep=''), 
            sep=",", row.names = FALSE, quote=FALSE)

write.table(wt_genes, file=paste(save_path, "genes/wt_gene_list.txt", sep=''), 
            sep=",", row.names = FALSE, quote=FALSE)
write.table(wt_only, file=paste(save_path, "genes/wt_only_gene_list.txt", sep=''), 
            sep=",", row.names = FALSE, quote=FALSE)
```

# Peak count distribution (Histograms)

Frequency of crosslink counts (in this case 1 peak = 1 crosslink) in a gene region.

```{r fig.width=10, message=FALSE, warning=FALSE}
binwidth <- 1
cutoff <- 1 

df_combined[c("sample", "Entrez.ID", "peak_count")] %>%
  distinct() %>%
  ggplot(aes(x = peak_count)) +
    geom_histogram(stat = "bin", binwidth = binwidth, fill = "cornflowerblue", col = "black") + 
    facet_wrap(~ sample) +
    ggtitle(sprintf('Distribution of PureCLIP peak count per sample with cut-off % s', cutoff)) +
  xlab("Number of peaks")

ggsave(paste(save_path, "histograms/pureclip_peak_count_distribution.png", sep=''))
```

## Relationship between peak count and gene length

Theoretically, the longer the gene, the more peaks (=crosslinks) it contains. Here, we check if this hypothesis holds true for our data.

```{r fig.height=10, fig.width=15}
cor.test(df_combined$peak_count, df_combined$gene_length)

# pureclip
df_combined[c("sample", "Entrez.ID", "peak_count", "gene_length")] %>%
  distinct() %>%
  ggplot(aes(x = peak_count, y = gene_length)) +
    geom_point(size = 0.1, shape = 1, col = "black") + 
    facet_wrap(~ sample) +
    ggtitle(sprintf('Relationship between gene_length and peak_count in PureCLIP data'), )

ggsave(paste(save_path, "histograms/pureclip_peak_genelength_histogram.png", sep=''))
```

# Gene types of genes (Barplots)

We now look at the individual genes instead of the peaks. Each gene (or Entrez.ID?) is therefore represented only once.

```{r fig.width=15, message=FALSE, warning=FALSE}
# each gene occurs only ONCE in its category regardless of peak intensity or count
df_combined %>%
  # get one row per gene (for each sample)
  {unique(.[, c("Entrez.ID", "Gene.Type", "sample")])} %>%
  group_by(sample, .drop = FALSE) %>%
  # count per gene type how many entrez ids it has
  add_count(Gene.Type, name = 'Entrez.ID') %>%
  # remove duplicate rows
  distinct() %>%
  # reorder for figure
  mutate(Gene.Type = fct_reorder2(Gene.Type, sample, Entrez.ID)) %>%
  
  # fraction plot
  ggplot(aes(x = sample, y = Entrez.ID)) +
    geom_bar(aes(fill = Gene.Type), width = 0.7, position="fill", stat="identity", colour="black") +
    theme(text = element_text(size=12)) + # change font size
    scale_fill_manual(values = myColor) + # change colors
    coord_flip() + # horizontal graph
    scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                       breaks = scales::breaks_pretty(10)) + # percentages
      ggtitle("Gene types of genes in fractions") +
    ylab("Fraction of Entrez IDs")

  # save figure
ggsave(paste(save_path, "gene_types_barplots/pureclip_genes_fraction.png", sep=''))

# each gene occurs only ONCE in its category regardless of peak intensity or count
df_combined %>%
  # get one row per gene (for each sample)
  {unique(.[, c("Entrez.ID", "Gene.Type", "sample")])} %>%
  group_by(sample, .drop = FALSE) %>%
  # count per gene type how many entrez ids it has
  add_count(Gene.Type, name = 'Entrez.ID') %>%
  # remove duplicate rows
  distinct() %>%
  # reorder for figure
  mutate(Gene.Type = fct_reorder2(Gene.Type, sample, Entrez.ID)) %>%

  # absolute plot
  ggplot(aes(x = sample, y = Entrez.ID)) +
    geom_col(aes(fill = Gene.Type), width = 0.7, colour="black") +
    geom_bar(position="fill", stat="identity") +
    theme(text = element_text(size=12)) +
    scale_fill_manual(values = myColor) +
    coord_flip() +
    scale_y_continuous(breaks = scales::breaks_pretty(10)) +
    ggtitle("Gene types of genes in counts") +
    ylab("Entrez ID count")

  # save figure
ggsave(paste(save_path, "gene_types_barplots/pureclip_genes_absolute.png", sep=''))
```

# Distance to TSS (Histograms)

HOMER reports the distance to the TSS.

```{r echo=FALSE, fig.align="center", fig.width=10, message=FALSE, warning=FALSE}
# calculate binwidth using Freedman-Diaconis
# also see: https://stats.stackexchange.com/questions/798/calculating-optimal-number-of-bins-in-a-histogram
binwidth <- 2 * IQR(na.omit(df_combined$Distance.to.TSS)) / length(na.omit(df_combined$Distance.to.TSS))^(1/3)

# histograms
df_combined %>%
  ggplot(aes(x = Distance.to.TSS, fill = as.factor(sample))) +
    geom_histogram(stat = "bin", binwidth = 100, fill = "cornflowerblue", col = "black") + 
    facet_wrap(~ sample) +
    scale_x_continuous(labels = comma , limits = c(-5000, 5000)
                       ) + # zoomed in
  ggtitle("Distance to TSS for each PureCLIP peak")
ggsave(paste(save_path, "histograms/pureclip_TSS_sep.png", sep=''))

# line graph of all samples
df_combined %>%
  ggplot(aes(x = Distance.to.TSS, fill = as.factor(sample))) +
    geom_line(stat = "bin", binwidth = 100, aes(color=sample)) + 
    scale_x_continuous(labels = comma , limits = c(-5000, 5000)
                       ) + # zoomed in
    ggtitle("Distance to TSS for each PureCLIP peak")
ggsave(paste(save_path, "histograms/pureclip_TSS.png", sep=''))

```

# Top genes

We can generate a list of the top genes, based on peak score, normalized peak count or a combination of the two.

```{r}
# e.g. based on normalized peak count:
df_combined %>% 
  group_by(sample)  %>% 
  slice_max(order_by = norm_peakcount_bylength, n = 100)
```

# Analyzing prominent genes

## Scatterplots

We can compare the genes based on e.g. normalized peak count by plotting gain-of-function against wild type samples in a scatterplot.

```{r echo=TRUE, fig.width=12, message=FALSE, warning=FALSE, gif.align="center"}
# average normalized peak count of entrez id is plotted
# x-axis: WT avg peak intensity
# y-axis GOF avg peak intensity

# this time, we only want entrez.IDs with a peak count equal to or higher than cutoff
cutoff <- 1
df_filtered <- df_combined[df_combined$peak_count >= cutoff,]

# create new df with norm peak counts per sample for each gene
couples <- df_filtered %>% 
  # group by id and sample
  group_by(Entrez.ID, Gene.Name, sample) %>% 
  # # calculate mean of peak score for each entrez id in each sample 
  summarise(AvgPeakScore=(mean(peak_count))) %>% 
  # transform tibble so gof 3 and wt 3 have their own columns
  pivot_wider(names_from = sample, values_from = AvgPeakScore) 

# make new column with Gene names: if Gene.Name is empty, replace with Entrez.ID
couples$id <- with(couples, ifelse(is.na(Gene.Name), Entrez.ID, Gene.Name))
# replace empty values by 0
couples <- mutate(couples, across(where(is.numeric), replace_na, 0))

# https://r-graph-gallery.com/275-add-text-labels-with-ggplot2.html
# https://plotly.com/ggplot2/hover-text-and-formatting/

# couple 3
ggplot(couples, aes(x=pureclip_wt_3, y=pureclip_gof_3)) +
  geom_point( alpha = 0.5, col = "black" ) +
  # geom_point(aes(text=Entrez.ID, Gene.Name), name='Entrez.ID', size=0.5, shape=5)
  geom_text_repel(
    data = couples %>% filter(pureclip_wt_3>median(couples$pureclip_wt_3) | pureclip_gof_3>median(couples$pureclip_gof_3)), # filter data first
    aes(label=id), size = 3, vjust="inward",hjust="inward"
    ) +
  xlab("Average normalized peak count in GoF 3") +
  ylab("Average normalized peak count in WT 3") +
  ggtitle("Genes associated with two or more peaks in GoF 3 and WT 3 samples")

ggsave(paste(save_path, sprintf("scatterplots/s3_cut_%s.png", cutoff), sep=''))

# couple 4
ggplot(couples, aes(x=pureclip_wt_4, y=pureclip_gof_4)) +
  geom_point( alpha = 0.5, col = "black" ) +
  geom_text_repel(
    data = couples %>% filter(pureclip_wt_4>median(couples$pureclip_wt_4) | pureclip_gof_4>median(couples$pureclip_gof_4)), # filter data first
    aes(label=id), size = 3, vjust="inward",hjust="inward"
    ) +
  xlab("Average normalized peak count in GoF 4") +
  ylab("Average normalized peak count in WT 4") +
  ggtitle("Genes associated with two or more peaks in GoF 4 and WT 4 samples")

ggsave(paste(save_path, sprintf("scatterplots/s4_cut_%s.png", cutoff), sep=''))

# couple 5
ggplot(couples, aes(x=pureclip_wt_5, y=pureclip_gof_5)) +
  geom_point( alpha = 0.5, col = "black" ) +
  geom_text_repel(
    data = couples %>% filter(pureclip_wt_5>median(couples$pureclip_wt_5) | pureclip_gof_5>median(couples$pureclip_gof_5)), # filter data first
    aes(label=id), size = 3, vjust="inward",hjust="inward"
    ) +
  xlab("Average normalized peak count in GoF 5") +
  ylab("Average normalized peak count in WT 5") +
  ggtitle("Genes associated with two or more peaks in GoF 5 and WT 5 samples")

ggsave(paste(save_path, sprintf("scatterplots/s5_cut_%s.png", cutoff), sep=''))
```

## Heatmaps

We can compare the samples based on e.g. normalized peak count by plotting them in heatmaps.

If `plot.new()` throws an error, create the `heatmaps` folder in the desired directory and run again.

```{r fig.height=20, fig.width=10, message=FALSE, warning=FALSE}
# create heatmaps directory so plot.new() does not throw an error
dir.create(paste(save_path, 'heatmaps', sep=''), showWarnings = FALSE)

# make palette
fc <- colorRampPalette(c("lightblue", "cornflowerblue", "darkblue"))

# making a copy of the dataframe
m_couples <- as.data.frame(couples)

# entrez.id = rownames
rownames(m_couples) <- m_couples$Entrez.ID
m_couples[,1] <- NULL

# split df into wt and gof
wt_coupled <- m_couples[,grepl("pureclip_wt_*", colnames(m_couples))]
gof_coupled <- m_couples[,grepl("pureclip_gof_*", colnames(m_couples))]

# # remove rows with only 0s
wt_coupled <- wt_coupled[apply(wt_coupled[,-1], 1, function(x) !all(x==0)),]
gof_coupled <- gof_coupled[apply(gof_coupled[,-1], 1, function(x) !all(x==0)),]

wt_coupled <- wt_coupled %>% 
  # remove rows with at least one 0 in it
  filter(if_all(pureclip_wt_3:pureclip_wt_5, ~ !.x  %in% 0)) %>%
  # order desc by wt_3
  
  # convert to matrix
  as.matrix()

gof_coupled <- gof_coupled %>% 
# remove rows with at least one 0 in it
  filter(if_all(pureclip_gof_3:pureclip_gof_5, ~ !.x  %in% 0)) %>%
  # order desc by gof_3
  
  # convert to matrix
  as.matrix()

# only genes that are present IN ALL 3 SAMPLES
png(file=paste(save_path, "heatmaps/wt_heatmap.png", sep=''))
heatmap(wt_coupled, 
        Colv = NA, 
        Rowv = NA, 
        scale = c('column'), 
        col = fc(20),
      )
# create the file
dev.off()

png(file=paste(save_path, "heatmaps/gof_heatmap.png", sep=''))
heatmap(gof_coupled, 
        Colv = NA, 
        Rowv = NA, 
        scale = c('column'), 
        col = fc(20)
        )
# create the file
dev.off()
```
